Notes

### 2023-09-07 Stats Rethinking/Ch3/Notes.qmd
Finished Ch3 Notes

>>>>

One such bound is the *compadability interval* (not to be confused with a confidence interval) which is an interval of posterior probability.

However, there are infinite intervals from which to choose any density (given density \< 1). Therefore, we should use the *Highest Point Density Interval* (HPDI) which, for a given probability mass, will give us the range with the most (dense) observations.

Still don't understand what a loss function is.

# 3.3 - Sampling to simulate prediction
